\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-06-27 chapters/1_intro.tex
Fix some mistakes and polish CS results

With our comparison experiments, performed both on 2D urban scenes from the CityScapes dataset and 3D electron microscopy image volumes of neurons, we evaluate the properties of the algorithms in our framework, focusing on their efficiency, robustness and tendency to over- or under-cluster.
We show that one of the new algorithms derived from our framework, based on an average linkage criterion, outperforms the previously known agglomeration methods expressed in the framework. It also achieves competitive performance on the challenging CREMI 2016 segmentation benchmark and is state-of-the-art on CityScapes when compared to other proposal-free methods.
Our code is available at \url{https://github.com/abailoni/GASP}.

\begin{figure}[t]
\centering
\includegraphics[width=\textwidth]{./figs/intro_image_v3.pdf} % left bottom right top
\caption{ Pipeline description: \textbf{(1)} Raw data from the CREMI 2016 neuron-segmentation challenge. \textbf{(2)} Some short- and long-range predictions of our CNN model, where white pixels represent boundary evidence. \textbf{(3)} Outputs of two agglomerative algorithms included in our proposed generalized clustering framework, with \emph{Sum} and \emph{Average} linkage criteria. The final clustering / instance segmentation is shown in 3a, overlaid with the raw image.  The  agglomeration order in 3b shows which pairs of neighboring pixels were merged first (white), later on (brown), or never (black). (\textbf{4}) Some iterations of \algname{} on toy graph examples with attractive/positive (green) and repulsive/negative (red) interactions. At each iteration, the yellow edge with highest interaction is contracted (orange arrows), until only negative edges are left in the graph.
\label{fig:intro_figure}}
\end{figure}

>>>>

With our comparison experiments, performed both on 2D urban scenes from the CityScapes dataset and 3D electron microscopy image volumes of neurons, we evaluate the properties of the algorithms in our framework, focusing on their efficiency, robustness and tendency to over- or under-cluster.
We show that one of the new algorithms derived from our framework, based on an average linkage criterion, outperforms the previously known agglomeration methods expressed in the framework. It also achieves competitive performance on the challenging CREMI 2016 segmentation benchmark and represents the best-performing proposal-free method on CityScapes.
Our code is available at \url{https://github.com/abailoni/GASP}.

\begin{figure}[t]
\centering
\includegraphics[width=\textwidth]{./figs/intro_image_v3.pdf} % left bottom right top
\caption{ Pipeline description: \textbf{(1)} Raw data from the CREMI 2016 neuron-segmentation challenge. \textbf{(2)} Some short- and long-range predictions of our CNN model, where white pixels represent boundary evidence. \textbf{(3)} Outputs of two agglomerative algorithms included in our proposed generalized clustering framework, with \emph{Sum} and \emph{Average} linkage criteria. The final clustering / instance segmentation is shown in 3a, overlaid with the raw image.  The  agglomeration order in 3b shows which pairs of neighboring pixels were merged first (white), later on (brown/red), or never (black). (\textbf{4}) Some iterations of \algname{} on toy graph examples with attractive/positive (green) and repulsive/negative (red) interactions. At each iteration, the yellow edge with highest interaction is contracted (orange arrows), until only negative edges are left in the graph.
\label{fig:intro_figure}}
\end{figure}

### 2019-06-27 chapters/3_algorithm.tex
Fix some mistakes and polish CS results

In Algorithm \ref{main_alg}, we provide simplified pseudo-code for the proposed \algname{} algorithm. \algname{} implements a bottom-up approach that starts by assigning each node to its own cluster and then iteratively merges pairs of adjacent clusters. The algorithm has two variants. The first one, with \texttt{addCannotLinkConstraints=False}, starts by merging clusters with the strongest attractive interaction and stops once the remaining clusters share only mutual by repulsive interactions (see iterations on toy graphs in block 4 of Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}}). After each merging iteration, the interaction between the merged cluster and its neighbors is updated according to one of the linkage criteria $\interact(S_u, S_v)$ listed in Table \ref{tab:linkage-criteria}.

@@

In Appendix \ref{sec:detailed_impl}, we comment on the algorithm's computational complexity $\mathcal{O}(N^2 \log N)$ and present our efficient implementation given by the edge contraction Algorithm \ref{detailed_alg} using a priority queue.

@@

Given a graph with both attractive and repulsive cues, an edge contraction algorithm with a sum update rule was pioneered in \cite{levinkov2017comparative,keuper2015efficient} (Table \ref{tab:linkage-criteria}, \emph{Sum} linkage). The authors present both a version with cannot-link constraints and one without, and then compare them with other greedy local-search algorithms approximating the multicut optimization problem.
The Mutex Watershed \cite{wolf2018mutex} is another signed graph partitioning algorithm that introduces dynamical cannot-link constraints. In Proposition \ref{prop:equiv_MWS} (see Appendix \ref{sec:appendix_abs_max}) we prove that, surprisingly, it can also be seen as an efficient implementation of \algname{} with \emph{Absolute maximum} linkage (see def. in Table \ref{tab:linkage-criteria}). Moreover, in Proposition \ref{prop:abs_max_cannot_link_property} we also prove that \algname{} with \emph{Abs Max} linkage returns the same clustering with or without enforcing cannot-link constraints.
On the other hand, to our knowledge, \emph{Average}, \emph{Max} or \emph{Min} linkage criteria have never been used for signed graph agglomerative algorithms or been combined with cannot-link constraints.

>>>>

In Algorithm \ref{main_alg}, we provide simplified pseudo-code for the proposed \algname{} algorithm. \algname{} implements a bottom-up approach that starts by assigning each node to its own cluster and then iteratively merges pairs of adjacent clusters. The algorithm has two variants. The first one, with \texttt{addCannotLinkConstraints=False}, starts by merging clusters with the strongest attractive interaction and stops once the remaining clusters share only mutual repulsive interactions (see iterations on toy graphs in block 4 of Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}}). After each merging iteration, the interaction between the merged cluster and its neighbors is updated according to one of the linkage criteria $\interact(S_u, S_v)$ listed in Table \ref{tab:linkage-criteria}.

@@

In Appendix \ref{sec:detailed_impl}, we comment on the algorithm's computational complexity $\mathcal{O}(N^2 \log N)$ and present our implementation given by the edge contraction Algorithm \ref{detailed_alg} based on a priority queue.

@@

Given a graph with both attractive and repulsive cues, an edge contraction algorithm with a sum update rule was pioneered in \cite{levinkov2017comparative,keuper2015efficient} (Table \ref{tab:linkage-criteria}, \emph{Sum} linkage). The authors present both a version with cannot-link constraints and one without, and then compare them with other greedy local-search algorithms approximating the multicut optimization problem.
The Mutex Watershed \cite{wolf2018mutex} is another signed graph partitioning algorithm that introduces dynamical cannot-link constraints. In Proposition \ref{prop:equiv_MWS} (see Appendix \ref{sec:appendix_abs_max}) we prove that, surprisingly, it can also be seen as an efficient implementation of \algname{} with \emph{Absolute maximum} linkage (def. in Table \ref{tab:linkage-criteria}). Moreover, in Proposition \ref{prop:abs_max_cannot_link_property} we also prove that \algname{} with \emph{Abs Max} linkage returns the same clustering with or without enforcing cannot-link constraints.
On the other hand, to our knowledge, \emph{Average}, \emph{Max} or \emph{Min} linkage criteria have never been used for signed graph agglomerative algorithms or been combined with cannot-link constraints.

### 2019-06-27 chapters/5_experiments_cityscapes.tex
Fix some mistakes and polish CS results

% !TEX root = ../agglo_clust_review.tex
\section{Experiments on CityScapes}\label{sec:cityscapes_exp}
We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images: 2975 for training, 500 for validation and 1525 for testing.
See Appendix \ref{sec:appendix_cityscapes} for more details on how we fine-tuned the state-of-the-art proposal-free pipeline proposed in GMIS \cite{liu2018affinity} by using a \emph{S\o resen-Dice} loss, similarly to \cite{wolf2018mutex}.
Results are summarized in Table \ref{tab:results_cityscapes_val} and Fig. \ref{fig:cityscapes}: \algname{} with \emph{Average} linkage achieves state-of-the-art results among proposal-free methods.
 Similarly to the previous experiments, other linkage criteria tend to over-cluster, like \emph{Abs Max}, or under-cluster and merge instances, like \emph{Sum}. The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by them, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.  
Appendix - Table \ref{tab:extended_results_cityscapes_val} includes the scores of all other tested \algname{} algorithms.
\captionsetup[subtable]{labelformat=simple, labelsep=space, justification=centering, singlelinecheck=off}
\renewcommand*{\thesubtable}{(\alph{subtable})}
\begin{table}[t]
\centering
\begin{subtable}{0.5 \textwidth}
    \centering
    \scriptsize
        \begin{tabular}{l|l|cc}
            Method & Agglomeration type & AP \\ \midrule
            PANet \cite{liu2018path} & - & \textbf{36.5} \\
            Mask R-CNN \cite{he2017mask} & - & 31.5 \\ \hline
             & \algname{} Average& 34.3 \\
             & \algname{} Average + Constraints & 33.9 \\
            \multirow{2}{*}{GMIS Model \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & 33.0 \\
             & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 \\
             & \algname{} Sum + Constraints  \cite{levinkov2017comparative} & 31.9  \\
             & \algname{} Sum \cite{keuper2015efficient} & 31.3 \\
        \end{tabular}
    \caption{CityScapes \emph{validation} set}
    \label{tab:results_cityscapes_val}
\end{subtable}\hfill
\begin{subtable}{0.46\textwidth}
\centering
    \scriptsize
\begin{tabular}{l|cc}
           Method & AP  & AP 50\% \\ \midrule
           PANet \cite{liu2018path} & \textbf{31.8} & \textbf{57.1} \\
           \textbf{Ours: GMIS Model + \algname{} Average} & 28.3 & 47.0 \\ 
           GMIS \cite{liu2018affinity} & 27.3 & 45.6 \\
           Mask R-CNN \cite{he2017mask} & 26.2 & 49.9 \\
           SGN \cite{liu2017sgn} & 25.0 & 44.9 \\
           DIN \cite{arnab2017pixelwise} & 20.0 & 38.8 \\
           DWT \cite{bai2017deep} & 19.4 & 35.3 \\
           InstanceCut \cite{kirillov2017instancecut} & 13.0 & 27.9 \\
        \end{tabular}
    \caption{CityScapes \emph{test} set}
    \label{tab:results_cityscapes_test}
\end{subtable}
\caption{Average Precision scores (higher is better) on the CityScapes dataset. \algname{} with \emph{Average} linkage combined with the GMIS Model \cite{liu2018affinity} represents the proposal-free method achieving the best results (May 2019). We only compare methods that did not use external data (e.g. COCO \cite{lin2014microsoft}) for training.}
\end{table}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{./figs/cityscapes_compare_4.pdf} % left bottom right top
\caption{Visual results given by different \algname{} linkage criteria on a crop of a CityScapes image}\label{fig:cityscapes}
\end{figure}

>>>>

% !TEX root = ../agglo_clust_review.tex
\captionsetup[subtable]{labelformat=simple, labelsep=space, justification=centering, singlelinecheck=off}
\renewcommand*{\thesubtable}{(\alph{subtable})}
\begin{table}[t]
\centering
\begin{subtable}{0.5 \textwidth}
    \centering
    \scriptsize
        \begin{tabular}{l|l|cc}
            Method & Agglomeration type & AP \\ \midrule
            PANet \cite{liu2018path} & - & \textbf{36.5} \\
            Mask R-CNN \cite{he2017mask} & - & 31.5 \\ \hline
             & \algname{} Average& 34.3 \\
             & \algname{} Average + Constraints & 33.9 \\
            \multirow{2}{*}{GMIS Model \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & 33.0 \\
             & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 \\
             & \algname{} Sum + Constraints  \cite{levinkov2017comparative} & 31.9  \\
             & \algname{} Sum \cite{keuper2015efficient} & 31.3 \\
        \end{tabular}
    \caption{CityScapes \emph{validation} set}
    \label{tab:results_cityscapes_val}
\end{subtable}\hfill
\begin{subtable}{0.46\textwidth}
\centering
    \scriptsize
\begin{tabular}{l|cc}
           Method & AP  & AP 50\% \\ \midrule
           PANet \cite{liu2018path} & \textbf{31.8} & \textbf{57.1} \\
           \textbf{Ours: GMIS Model + \algname{} Average} & 28.3 & 47.0 \\ 
           GMIS \cite{liu2018affinity} & 27.3 & 45.6 \\
           Mask R-CNN \cite{he2017mask} & 26.2 & 49.9 \\
           SGN \cite{liu2017sgn} & 25.0 & 44.9 \\
           DIN \cite{arnab2017pixelwise} & 20.0 & 38.8 \\
           DWT \cite{bai2017deep} & 19.4 & 35.3 \\
           InstanceCut \cite{kirillov2017instancecut} & 13.0 & 27.9 \\
        \end{tabular}
    \caption{CityScapes \emph{test} set}
    \label{tab:results_cityscapes_test}
\end{subtable}
\caption{Average Precision scores (higher is better) on the CityScapes dataset. \algname{} with \emph{Average} linkage combined with the GMIS Model \cite{liu2018affinity} represents the proposal-free method achieving the best results (May 2019). In order to have a fair comparison, we only compare methods that did not use external data (e.g. COCO \cite{lin2014microsoft}) for training. In Table (a) on the left we distinguish between proposal-based and proposal-free methods.}\label{tab:results_cityscapes}
\end{table}

\section{Experiments on CityScapes}\label{sec:cityscapes_exp}
We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images: 2975 for training, 500 for validation and 1525 for testing.
We used the pipeline proposed in GMIS \cite{liu2018affinity}, representing the proposal-free method performing best on the dataset. The pipeline consists of two CNN with similar structures, one predicting pixel level semantic scores and the other predicting pixel affinities between instances. The code and the model are publicly available, so we provided its output affinities as input to \algname{}.
In Appendix \ref{sec:appendix_cityscapes} we present how we fine-tuned the model by using a \emph{S\o resen-Dice} loss, similarly to \cite{wolf2018mutex}.

Results are summarized in Table \ref{tab:results_cityscapes} and Fig. \ref{fig:cityscapes}: the best scores are achieved by PANet \cite{liu2018path}, which is a proposal-based method strongly related to Mask R-CNN. \algname{} with \emph{Average} linkage achieves competitive results and outperforms all previously proposed proposal-free methods. Similarly to the experiments on neuron segmentation, other linkage criteria tend to over-cluster, like \emph{Abs Max}, or under-cluster and merge instances, like \emph{Sum}. The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and when we applied it to the affinities predicted by our fine-tuned model it achieved an AP score of 33.0 on the validation set, which is worse than the original value 34.1 reported in \cite{liu2018affinity}. This is probably due to the fact that the agglomeration MultiStepHAC was tailored to the output affinities of the original model. 
Table \ref{tab:extended_results_cityscapes_val} in Appendix includes the scores of all other tested \algname{} algorithms.
\begin{figure}
\centering
\includegraphics[width=\textwidth]{./figs/cityscapes_compare_4.pdf} % left bottom right top
\caption{Visual results given by different \algname{} linkage criteria on a crop of a CityScapes image}\label{fig:cityscapes}
\end{figure}

### 2019-06-27 chapters/5_experiments_intro.tex
Fix some mistakes and polish CS results

EM segmentation is commonly performed by first predicting 
boundary pixels \cite{beier2017multicut,ciresan2012deep} or undirected affinities \cite{wolf2018mutex,lee2017superhuman,funke2018large}, which represent how likely it is for a pair of pixels to belong to the same neuron segment. 
The affinities do not have to be limited to immediately adjacent pixels
Thus, similarly to \cite{lee2017superhuman}, we train a CNN to predict both short- and long-range affinities
and use them as edge weights of a 3D grid graph, where each node represents a pixel/voxel of the volume image.

>>>>

EM segmentation is commonly performed by first predicting 
boundary pixels \cite{beier2017multicut,ciresan2012deep} or undirected affinities \cite{wolf2018mutex,lee2017superhuman,funke2018large}, which represent how likely it is for a pair of pixels to belong to the same neuron segment. 
The affinities do not have to be limited to immediately adjacent pixels.
Thus, similarly to \cite{lee2017superhuman}, we train a CNN to predict both short- and long-range affinities
and use them as edge weights of a 3D grid graph, where each node represents a pixel/voxel of the volume image.

### 2019-06-27 chapters/supplementary.tex
Fix some mistakes and polish CS results

\paragraph{THRESH and WSDT} The basic post-processing methods we consider cannot take long-range affinities into account, so we only consider direct neighbors affinities and generate a boundary map by taking an average over the 3 directions. Based on this boundary map, we run connected components (THRESH) and we also introduce seeds at the maxima of the smoothed distance transform (WSDT). For WSDT, the degree of smoothing was optimized such that each region receives as few seeds as possible, without however causing severe under-segmentation. Due to the anisotropy of the data, we generate 2D WSDT superpixels by considering each 2D image in the stack singularly.

@@

\subsection{\algname{} on the full CREMI dataset} \label{sec:appendix_exps_full_cremi}
 \paragraph{Pre-merge processing} For the predictions on the full dataset from the CREMI challenge, we used  the padded volumes provided by the challenge. The crops on which we performed a prediction have a size of $1500\times1500\times127=2.86\cdot 10^8$ voxels or larger. Building a graph with $10^8$ nodes can easily incur a large use of memory, so we decided to perform a preprocessing step by initially merging some nodes together. Simply down-sampling the predictions of the CNN would have led to a loss of resolution and performances in the most difficult parts of the dataset. Thus, we decided to pre-merge the most connected components of the graph that would be anyway clustered during the first iterations of \algname{}. To do this, we used a simple approach: we generated a boundary probability map by taking for each voxel an average over affinities in all directions (both short- and long-range ones) and we run THRESH with a conservative threshold parameter to find the connected components. With this approach, pixels are pre-clustered only when they are far away (in all directions) from predicted boundaries. 
 To make sure that in this preprocessing step different neurons are never merged together by mistake, we intersected the segments given by THRESH with the segments given by WSDT. 
 In our experiments, the use of this preprocessing method did not introduce any major changes in the final segmentations and scores achieved, but significantly reduced the runtime. Moreover, to reduce the runtime and memory requirements even further, we used only 10 \% of the long-range connections in the pixel-graph, since adding all of them did not improve the scores.

@@

\begin{table}[t]
\centering
    \footnotesize
        \begin{tabular}{l|c|c|c|c|c}
          \algname{} linkage & \makecell{CREMI-Score\\(higher better)}  & \makecell{Rand-Score\\(higher better)} & \makecell{VI-merge\\(lower better)} & \makecell{VI-split\\(lower better)} & \makecell{Runtime\\(lower better)} \\ \midrule
Average & \textbf{0.226} & \textbf{0.936} & 0.315 & 0.494 & 3.49 $\cdot$ 10$^4$ \\
Sum + CLC \cite{levinkov2017comparative} & 0.282 & 0.906 & 0.358 & 0.510 & 4.64 $\cdot$ 10$^4$ \\
Abs Max \cite{wolf2018mutex} & 0.322 & 0.897 & 0.286 & 0.735 & 1.24 $\cdot$ 10$^4$ \\
Max + CLC & 0.324 & 0.893 & 0.292 & 0.698 & 6.31 $\cdot$ 10$^4$ \\
Sum \cite{keuper2015efficient} & 0.334 & 0.872 & 0.461 & 0.444 & 4.74 $\cdot$ 10$^4$ \\
Average + CLC & 0.563 & 0.772 & 0.259  & 1.142 & 2.95 $\cdot$ 10$^4$ \\
Min & 2.522 & 0.030 & \textbf{0.197} & 6.365 & 2.97 $\cdot$ 10$^3$ \\
Min + CLC & 2.522 & 0.030 & \textbf{0.197}  & 6.365 & 4.77 $\cdot$ 10$^3$ \\
Max & 2.626 & 0.028 & 7.069 & \textbf{0.026} & \textbf{6.04 $\cdot$ 10$^\mathbf{2}$} \\
        \end{tabular}
        \vspace*{1.1em}
    \caption{Performances achieved by different versions of \algname{} on the CREMI 2016 training set. 
    CREMI-Score \cite{cremiChallenge}, is given by a combination of the Adapted Rand-Score (Rand-Score) and the Variation of Information Score for under-clustering (VI-merge) and over-clustering (VI-split) \cite{arganda2015crowdsourcing}.
    CLC stands for cannot-link constraints. For all algorithms, the chosen value of bias parameter was $\beta = 0$. We used a machine with CPU Intel(R) Xeon(R) X5650  @ 2.67GHz for our comparison experiments.}
    \label{tab:extended_results_cremi}
\end{table}

@@

\subsection{Fine-tuning the GMIS pipeline on CityScapes} \label{sec:appendix_cityscapes}
For our experiments, we used the model from GMIS \cite{liu2018affinity} that is publicly available. The instance-branch of the model was trained with a Binary Cross-Entropy loss, but we noticed how the short-range affinities were biased towards high probabilities, so that a strong short-range boundary evidence was never predicted by the model. In \cite{liu2018affinity}, they handle this problem by proposing a modified version of HAC that is done in stages (MultiStepHAC): initially only short-range affinities are used to run HAC and a low threshold in the hierarchy is chosen to define a first clustering; then a new HAC problem including long-range affinities is  initialized with the first clustering; in the method proposed by \cite{liu2018affinity}, these steps are repeated three times.

Since MultiStepHAC is a rather complex post-processing method that requires to tune several hyper-parameters, we opted for a different approach to solve the problem of the unbalanced affinities. We added two 1x1 convolutional layers to the instance-branch model and trained them by using the same loss used for example by \cite{wolf2018mutex} and is based on the S\o resen-Dice coefficient \cite{dice1945measures,sorensen1948method}. Compared to Hamming-distance based loss like Binary Cross-Entropy or Mean Squared Error, the advantage of this loss is its being robust against prediction and / or target sparsity, that is a desirable quality in this application since boundaries between instances can be sparse. 
During training, all the affinities involving at least one pixel belonging to the background were ignored in the loss. In this way, these last two layers specialized in improving the predictions of boundary evidence between adjacent instances (especially those belonging to the same class). We then considered an average of these new fine-tuned affinities with the original unbalanced ones predicted by the model. During the fine-tuning process, only the parameters in the last two layers were updated.

Before to apply \algname{}, we performed a parameter-search for the bias $\beta$ defined in \ref{eq:mappings}. Table \ref{tab:extended_results_cityscapes_val} lists the best-case performances for each of the methods with the chosen bias $\beta$: note that depending on the version of \algname{}, it was necessary to bias more or less the predicted edge weights.

The semantic categories are assigned to each instance in the same way proposed by \cite{liu2018affinity}, i.e. with a majority vote based on the semantic output of the model. Moreover, we use the same method  proposed by \cite{liu2018affinity} to compute the edge weights of the graph by combining both semantic and instance outputs.

>>>>

\paragraph{THRESH and WSDT} The basic post-processing methods we consider cannot take long-range affinities into account, so we only consider direct neighbors affinities and generate a boundary map by taking an average over the 3 directions. Based on this boundary map, we run connected components (THRESH) and we also run a watershed algorithm  seeded at the maxima of the smoothed distance transform (WSDT). For WSDT, the degree of smoothing was optimized such that each region receives as few seeds as possible, without however causing severe under-segmentation. Due to the anisotropy of the data, we generate 2D WSDT superpixels by considering each 2D image in the stack singularly.

@@

\subsection{\algname{} on the full CREMI dataset} \label{sec:appendix_exps_full_cremi}
 \paragraph{Pre-merge processing} For the predictions on the full dataset from the CREMI challenge, we used  the padded volumes provided by the challenge. The crops on which we performed a prediction have a size of $1500\times1500\times127=2.86\cdot 10^8$ voxels or larger. Building a graph with $10^8$ nodes can easily incur a large use of memory, so we decided to perform a preprocessing step by initially merging some nodes together. Simply down-sampling the predictions of the CNN would have led to a loss of resolution and performances in the most difficult parts of the dataset. Thus, we decided to pre-merge the most connected components of the graph that would be anyway clustered during the first iterations of \algname{}. To do this, we used a simple approach: we generated a boundary probability map by taking for each voxel an average over affinities in all directions (both short- and long-range ones) and we run THRESH with a conservative threshold parameter to find the connected components. With this approach, pixels are pre-clustered only when they are far away (in all directions) from predicted boundaries. 
 To make sure that in this preprocessing step different neurons are never merged together by mistake, we intersected the segments given by THRESH with the segments given by WSDT. 
 We tested \algname{} both on the full grid-graph and on this preprocessed graph and we did not notice any major differences in the final clustering or achieved scores, although the version with a pre-processed graph was significantly faster. To reduce the runtime and memory requirements even further, we used only 10 \% of the long-range connections in the pixel-graph, since adding all of them did not improve the scores.

@@

\begin{table}[t]
\centering
    \footnotesize
        \begin{tabular}{l|c|c|c|c|c}
          \algname{} linkage & \makecell{CREMI-Score\\(higher better)}  & \makecell{Rand-Score\\(higher better)} & \makecell{VI-merge\\(lower better)} & \makecell{VI-split\\(lower better)} & \makecell{Runtime\\(lower better)} \\ \midrule
Average & \textbf{0.226} & \textbf{0.936} & 0.315 & 0.494 & 3.49 $\cdot$ 10$^4$ \\
Sum + CLC \cite{levinkov2017comparative} & 0.282 & 0.906 & 0.358 & 0.510 & 4.64 $\cdot$ 10$^4$ \\
Abs Max \cite{wolf2018mutex} & 0.322 & 0.897 & 0.286 & 0.735 & 1.24 $\cdot$ 10$^4$ \\
Max + CLC & 0.324 & 0.893 & 0.292 & 0.698 & 6.31 $\cdot$ 10$^4$ \\
Sum \cite{keuper2015efficient} & 0.334 & 0.872 & 0.461 & 0.444 & 4.74 $\cdot$ 10$^4$ \\
Average + CLC & 0.563 & 0.772 & 0.259  & 1.142 & 2.95 $\cdot$ 10$^4$ \\
Min & 2.522 & 0.030 & \textbf{0.197} & 6.365 & 2.97 $\cdot$ 10$^3$ \\
Min + CLC & 2.522 & 0.030 & \textbf{0.197}  & 6.365 & 4.77 $\cdot$ 10$^3$ \\
Max & 2.626 & 0.028 & 7.069 & \textbf{0.026} & \textbf{6.04 $\cdot$ 10$^\mathbf{2}$} \\
        \end{tabular}
        \vspace*{1.1em}
    \caption{Performances achieved by different versions of \algname{} on the CREMI 2016 training set. 
    CREMI-Score \cite{cremiChallenge}, is given by a combination of the Adapted Rand-Score (Rand-Score) and the Variation of Information Score for under-clustering (VI-merge) and over-clustering (VI-split) \cite{arganda2015crowdsourcing}.
    CLC stands for cannot-link constraints. For all algorithms, the chosen value of bias parameter was $\beta = 0$. We used a machine with CPU Intel(R) Xeon(R) E7-4870 @ 2.40GHz for our comparison experiments.}
    \label{tab:extended_results_cremi}
\end{table}

@@

\subsection{Fine-tuning the GMIS pipeline on CityScapes} \label{sec:appendix_cityscapes}
For our experiments, we used the model from GMIS \cite{liu2018affinity} that is publicly available. 
The model consists of two neural networks with similar structures, one predicting pixel level semantic scores and the other predicting pixel affinities between instances. We also used all the affinity post-processing methods proposed in \cite{liu2018affinity}, e.g. excluding background, resizing regions of interest or the proposed "affinity-refinement" method, which combines semantic and instance outputs. 
 The instance-branch of the model was trained with a Binary Cross-Entropy loss, but we noticed how the short-range affinities were biased towards high probabilities, so that a strong short-range boundary evidence was never predicted by the model. In \cite{liu2018affinity}, they handle this problem by proposing a modified version of HAC that is done in stages (MultiStepHAC): initially only short-range affinities are used to run HAC and a low threshold in the hierarchy is chosen to define a first clustering; then a new HAC problem including long-range affinities is  initialized with the first clustering; in the method proposed by \cite{liu2018affinity}, these steps are repeated three times.

Since MultiStepHAC is a rather complex post-processing method that requires to tune several hyper-parameters, we opted for a different approach to solve the problem of the unbalanced affinities. We added two 1x1 convolutional layers to the instance-branch model and trained them by using the same loss used by \cite{wolf2018mutex} and is based on the S\o resen-Dice coefficient \cite{dice1945measures,sorensen1948method}. Compared to Hamming-distance based loss like Binary Cross-Entropy or Mean Squared Error, the advantage of this loss is its being robust against prediction and / or target sparsity, that is a desirable quality in this application since boundaries between instances can be sparse. 
During training, all the affinities involving at least one pixel belonging to the background were ignored in the loss. In this way, these last two layers specialized in improving the predictions of boundary evidence between adjacent instances (especially those belonging to the same class). We then considered an average of these new fine-tuned affinities with the ones predicted by the original model. During the fine-tuning process, only the parameters of the last two convolutional layers were updated.

Before to apply \algname{}, we performed a parameter-search for the bias $\beta$ defined in \ref{eq:mappings}. Table \ref{tab:extended_results_cityscapes_val} lists the best-case performances for each of the methods: note that depending on the \algname{} linkage criterion, it was necessary to bias more or less the predicted edge weights.

The semantic categories are assigned to each instance in the same way proposed by \cite{liu2018affinity}, i.e. with a majority vote based on the semantic output of the model.
